### 2020-08-25 2_task_bench.tex
Fix typo.

Listing~\ref{lst:code-sample} shows an excerpt from the Task Bench
implementation in MPI. Methods of the \lstinline{Graph} object
\lstinline{g} are provided by Task Bench's core API and are shared
among all implementations. These methods are summarized in
Table~\ref{tab:api}. The MPI implementation follows the style of
communicating sequential processes (CSP), and executes a set of send
and receive calls (lines 24 and 16, respectively) followed by
executing the task body (line 32). Despite MPI having no notion of
task, the execution of a task graph maps into the CSP style in a
straightforward way. The implementation is both simple and efficient,
but do to the choice of CSP makes no attempt to exploit task
parallelism, and leaves performance on the table when executing task
graphs with load imbalance or communication. Note the excerpt is
simplified for presentation and the full implementation is more
general and provides additional optimizations.

>>>>

Listing~\ref{lst:code-sample} shows an excerpt from the Task Bench
implementation in MPI. Methods of the \lstinline{Graph} object
\lstinline{g} are provided by Task Bench's core API and are shared
among all implementations. These methods are summarized in
Table~\ref{tab:api}. The MPI implementation follows the style of
communicating sequential processes (CSP), and executes a set of send
and receive calls (lines 24 and 16, respectively) followed by
executing the task body (line 32). Despite MPI having no notion of
task, the execution of a task graph maps into the CSP style in a
straightforward way. The implementation is both simple and efficient,
but due to the choice of CSP makes no attempt to exploit task
parallelism, and leaves performance on the table when executing task
graphs with load imbalance or communication. Note the excerpt is
simplified for presentation and the full implementation is more
general and provides additional optimizations.
